Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-01-05 analysis/paper/paper.tex
changed files for readability

  \title{Assessment of the KLGO Coastal Waterbird Survey Monitoring Program}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{true \\ true}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{10 December, 2018}

@@

This report was generated on 2018-12-10 13:33:40 using the following
computational environment and dependencies:

\begin{verbatim}
#>  setting  value                       
#>  version  R version 3.5.1 (2018-07-02)
#>  system   x86_64, linux-gnu           
#>  ui       X11                         
#>  language (EN)                        
#>  collate  en_US.UTF-8                 
#>  tz       EST5EDT                     
#>  date     2018-12-10                  
#> 
#>  package    * version date       source        
#>  assertthat   0.2.0   2017-04-11 CRAN (R 3.3.1)
#>  backports    1.1.2   2017-12-13 CRAN (R 3.5.0)
#>  base       * 3.5.1   2018-09-10 local         
#>  bindr        0.1.1   2018-03-13 CRAN (R 3.5.0)
#>  bindrcpp   * 0.2.2   2018-03-29 CRAN (R 3.5.0)
#>  colorspace   1.3-2   2016-12-14 CRAN (R 3.5.0)
#>  compiler     3.5.1   2018-09-10 local         
#>  crayon       1.3.4   2017-09-16 CRAN (R 3.3.1)
#>  datasets   * 3.5.1   2018-09-10 local         
#>  DBI          1.0.0   2018-05-02 CRAN (R 3.5.0)
#>  dbplyr     * 1.2.2   2018-07-25 CRAN (R 3.5.0)
#>  devtools     1.13.6  2018-06-27 CRAN (R 3.5.0)
#>  digest       0.6.17  2018-09-12 CRAN (R 3.5.0)
#>  dplyr      * 0.7.6   2018-06-29 CRAN (R 3.5.0)
#>  evaluate     0.11    2018-07-17 CRAN (R 3.5.0)
#>  farver       1.1.0   2018-11-20 CRAN (R 3.5.1)
#>  ggforce    * 0.1.3   2018-07-07 CRAN (R 3.5.1)
#>  ggplot2    * 3.0.0   2018-07-03 CRAN (R 3.5.0)
#>  ggthemes   * 4.0.1   2018-08-24 CRAN (R 3.5.1)
#>  glue         1.3.0   2018-07-17 CRAN (R 3.5.0)
#>  graphics   * 3.5.1   2018-09-10 local         
#>  grDevices  * 3.5.1   2018-09-10 local         
#>  grid         3.5.1   2018-09-10 local         
#>  gtable       0.2.0   2016-02-26 CRAN (R 3.5.0)
#>  hms          0.4.2   2018-03-10 CRAN (R 3.5.0)
#>  htmltools    0.3.6   2017-04-28 CRAN (R 3.5.0)
#>  knitr        1.20    2018-02-20 CRAN (R 3.5.0)
#>  lazyeval     0.2.1   2017-10-29 CRAN (R 3.5.0)
#>  lubridate  * 1.7.4   2018-04-11 CRAN (R 3.5.0)
#>  magrittr     1.5     2014-11-22 CRAN (R 3.1.2)
#>  MASS         7.3-50  2018-04-30 CRAN (R 3.5.1)
#>  memoise      1.1.0   2017-04-21 CRAN (R 3.4.3)
#>  methods    * 3.5.1   2018-09-10 local         
#>  munsell      0.5.0   2018-06-12 CRAN (R 3.5.0)
#>  pillar       1.3.0   2018-07-14 CRAN (R 3.5.0)
#>  pkgconfig    2.0.2   2018-08-16 CRAN (R 3.5.0)
#>  plyr         1.8.4   2016-06-08 CRAN (R 3.5.0)
#>  purrr        0.2.5   2018-05-29 CRAN (R 3.5.0)
#>  R6           2.2.2   2017-06-17 CRAN (R 3.3.1)
#>  Rcpp         0.12.18 2018-07-23 CRAN (R 3.5.0)
#>  readr      * 1.1.1   2017-05-16 CRAN (R 3.5.0)
#>  rlang        0.2.2   2018-08-16 CRAN (R 3.5.0)
#>  rmarkdown    1.10    2018-06-11 CRAN (R 3.5.0)
#>  rprojroot    1.3-2   2018-01-03 CRAN (R 3.5.0)
#>  scales       1.0.0   2018-08-09 CRAN (R 3.5.0)
#>  stats      * 3.5.1   2018-09-10 local         
#>  stringi      1.2.4   2018-07-20 CRAN (R 3.5.0)
#>  stringr    * 1.3.1   2018-05-10 CRAN (R 3.5.0)
#>  tibble       1.4.2   2018-01-22 CRAN (R 3.5.0)
#>  tidyr      * 0.8.1   2018-05-18 CRAN (R 3.5.0)
#>  tidyselect   0.2.4   2018-02-26 CRAN (R 3.5.0)
#>  tools        3.5.1   2018-09-10 local         
#>  tweenr       1.0.0   2018-09-27 CRAN (R 3.5.1)
#>  units        0.6-0   2018-06-09 CRAN (R 3.5.0)
#>  utils      * 3.5.1   2018-09-10 local         
#>  withr        2.1.2   2018-03-15 CRAN (R 3.5.0)
#>  yaml         2.2.0   2018-07-25 CRAN (R 3.5.0)
\end{verbatim}

>>>>

  \title{Assessment of the KLGO Coastal Waterbird Survey Monitoring Program}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{true \\ true}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{11 December, 2018}

@@

This report was generated on 2018-12-11 18:15:51 using the following
computational environment and dependencies:

\begin{verbatim}
#>  setting  value                       
#>  version  R version 3.5.1 (2018-07-02)
#>  system   x86_64, linux-gnu           
#>  ui       X11                         
#>  language (EN)                        
#>  collate  en_US.UTF-8                 
#>  tz       EST5EDT                     
#>  date     2018-12-11                  
#> 
#>  package    * version date       source        
#>  assertthat   0.2.0   2017-04-11 CRAN (R 3.3.1)
#>  backports    1.1.2   2017-12-13 CRAN (R 3.5.0)
#>  base       * 3.5.1   2018-09-10 local         
#>  bindr        0.1.1   2018-03-13 CRAN (R 3.5.0)
#>  bindrcpp   * 0.2.2   2018-03-29 CRAN (R 3.5.0)
#>  colorspace   1.3-2   2016-12-14 CRAN (R 3.5.0)
#>  compiler     3.5.1   2018-09-10 local         
#>  crayon       1.3.4   2017-09-16 CRAN (R 3.3.1)
#>  datasets   * 3.5.1   2018-09-10 local         
#>  DBI          1.0.0   2018-05-02 CRAN (R 3.5.0)
#>  dbplyr     * 1.2.2   2018-07-25 CRAN (R 3.5.0)
#>  devtools     1.13.6  2018-06-27 CRAN (R 3.5.0)
#>  digest       0.6.17  2018-09-12 CRAN (R 3.5.0)
#>  dplyr      * 0.7.6   2018-06-29 CRAN (R 3.5.0)
#>  evaluate     0.11    2018-07-17 CRAN (R 3.5.0)
#>  farver       1.1.0   2018-11-20 CRAN (R 3.5.1)
#>  ggforce    * 0.1.3   2018-07-07 CRAN (R 3.5.1)
#>  ggplot2    * 3.0.0   2018-07-03 CRAN (R 3.5.0)
#>  ggthemes   * 4.0.1   2018-08-24 CRAN (R 3.5.1)
#>  glue         1.3.0   2018-07-17 CRAN (R 3.5.0)
#>  graphics   * 3.5.1   2018-09-10 local         
#>  grDevices  * 3.5.1   2018-09-10 local         
#>  grid         3.5.1   2018-09-10 local         
#>  gtable       0.2.0   2016-02-26 CRAN (R 3.5.0)
#>  hms          0.4.2   2018-03-10 CRAN (R 3.5.0)
#>  htmltools    0.3.6   2017-04-28 CRAN (R 3.5.0)
#>  knitr        1.20    2018-02-20 CRAN (R 3.5.0)
#>  lazyeval     0.2.1   2017-10-29 CRAN (R 3.5.0)
#>  lubridate  * 1.7.4   2018-04-11 CRAN (R 3.5.0)
#>  magrittr     1.5     2014-11-22 CRAN (R 3.1.2)
#>  MASS         7.3-50  2018-04-30 CRAN (R 3.5.1)
#>  memoise      1.1.0   2017-04-21 CRAN (R 3.4.3)
#>  methods    * 3.5.1   2018-09-10 local         
#>  munsell      0.5.0   2018-06-12 CRAN (R 3.5.0)
#>  pillar       1.3.0   2018-07-14 CRAN (R 3.5.0)
#>  pkgconfig    2.0.2   2018-08-16 CRAN (R 3.5.0)
#>  plyr         1.8.4   2016-06-08 CRAN (R 3.5.0)
#>  purrr        0.2.5   2018-05-29 CRAN (R 3.5.0)
#>  R6           2.2.2   2017-06-17 CRAN (R 3.3.1)
#>  Rcpp         0.12.18 2018-07-23 CRAN (R 3.5.0)
#>  readr      * 1.1.1   2017-05-16 CRAN (R 3.5.0)
#>  rlang        0.2.2   2018-08-16 CRAN (R 3.5.0)
#>  rmarkdown    1.10    2018-06-11 CRAN (R 3.5.0)
#>  rprojroot    1.3-2   2018-01-03 CRAN (R 3.5.0)
#>  scales       1.0.0   2018-08-09 CRAN (R 3.5.0)
#>  stats      * 3.5.1   2018-09-10 local         
#>  stringi      1.2.4   2018-07-20 CRAN (R 3.5.0)
#>  stringr    * 1.3.1   2018-05-10 CRAN (R 3.5.0)
#>  tibble       1.4.2   2018-01-22 CRAN (R 3.5.0)
#>  tidyr      * 0.8.1   2018-05-18 CRAN (R 3.5.0)
#>  tidyselect   0.2.4   2018-02-26 CRAN (R 3.5.0)
#>  tools        3.5.1   2018-09-10 local         
#>  tweenr       1.0.0   2018-09-27 CRAN (R 3.5.1)
#>  units        0.6-0   2018-06-09 CRAN (R 3.5.0)
#>  utils      * 3.5.1   2018-09-10 local         
#>  withr        2.1.2   2018-03-15 CRAN (R 3.5.0)
#>  yaml         2.2.0   2018-07-25 CRAN (R 3.5.0)
\end{verbatim}
